---
title: "japan_weather_index_xkcd.r"
author: "Ryo Nakagawara"
date: "Wed Nov 22 01:18:06 2017"
output:
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

In the past week or so, XKCD graphs of the most comfortable place to live in -X- have been popping up over social media. Jumping onto this trend, I will do one for JAPAN, where I was born!

Let's get started!

```{r }
library(dplyr)
library(riem)

riem_stations(network = "JP__ASOS")

```

Using Maelle Salmon's `riem` package we can look up weather data from all over the world collected at airport weather stations. We can see that there are 136 different stations (and airports) in Japan's network! From the `ID` we can also see that the airports are coded in the **ICAO** standard rather than the **IATA** standard, this will come into play later!

For which exact cities to choose, I took a note from Maelle's article where she searched for the cities with the busiest airports. This makes sense as the weather data we will gather and the airport data will then have a similar column on which we can join on!

My source was from the **Ministry of Land, Infrastructure, Transport and Tourism (MLIT)** statistics on Japan's busiest airports (in terms of total passenger traffic), which has been copied onto everybody's favorite "knowledge bank", Wikipedia ([Link!](https://en.wikipedia.org/wiki/List_of_the_busiest_airports_in_Japan))! The most recent list is from 2015 and although I could look up more recent figures I don't think two years would make such a big difference (... and I'm lazy). 

I load up my favorite web scraping package, `rvest` and gather the list of airports! (For a step-by-step intro to web-scraping using R, check out my other blog post [here](https://ryo-n7.github.io/2017-09-18-global-peace-index/)!)

```{r}
library(rvest)

url <- "https://en.wikipedia.org/wiki/List_of_the_busiest_airports_in_Japan"

# css selector: "table.wikitable:nth-child(10)"

japan_airports <- url %>% 
  read_html() %>% 
  html_node("table.wikitable:nth-child(10)") %>% 
  html_table()

glimpse(japan_airports)

```

In the table, the airport codes in both IATA and ICAO format are in a single column separated by a slash.

We can use the `separate()` function from the `tidyr` package to separate the airport code column into the respective IATA and ICAO codes.

The regex for a literal slash is "\\/", remember that you need to escape twice!

```{r Separate IATA and ICAO codes}
# Separate IATA and ICAO codes:
library(tidyr) # use separate() function!

japan_airports <- japan_airports %>% 
  separate(`IATA/ICAO`, c("IATA", "ICAO"), "\\/")

japan_airports <- japan_airports %>% rename(City = `City\nserved`)

glimpse(japan_airports)

```

Now let's **save** our handy dataset so we do not have to re-run web scraping every time!

```{r}

write.csv(japan_airports, "~/R_materials/japan_weather_xkcd/japan_airports.csv")

```

And when we want to start off where we left off we can use `read.csv()` to load our data set without have to go through the web scraping code!

```{r}

japan_airports <- read.csv("~/R_materials/japan_weather_xkcd/japan_airports.csv", 
         stringsAsFactors = FALSE)

```

Back to our analysis!

47 prefectures, top 50 airports, let's just start by looking at the weather data for all
of them instead of taking only top 25/10/whatever airports. We can shorten the list if that's too many data points on the plot or map later on!

```{r}

jp_airport_codes <- japan_airports %>% select(Airport, City, ICAO)

```

# taking code from Maelle Salmon's post 
# >>> use purrr::map_df to call riem::measures on each airport code!
I've been slowly trying to incorporate more purrr into my data analysis tool set, so it's great that I get another chance to use it here!

Basically what purrr is doing is:

*
*
*
*

Let's see it in action!

```{r purrr for create df with data for each weather station}
library(purrr)
library(riem)

# big file, will take a minute or so!
summer_weather <- map_df(jp_airport_codes$ICAO, riem::riem_measures,
                                date_start = "2017-06-01",
                                date_end = "2017-08-31")

write.csv(summer_weather, "~/R_materials/japan_weather_xkcd/summer_weather.csv")

winter_weather <- map_df(jp_airport_codes$ICAO, riem::riem_measures,
                                date_start = "2016-12-01",
                                date_end = "2017-02-28")

write.csv(winter_weather, "~/R_materials/japan_weather_xkcd/winter_weather.csv")

```

READ IN DATA >>> DONT RERUN RIEM CODE EVERY TIME

```{r save summer+winter_weather.csv}

summer_weather <- read.csv("summer_weather.csv", stringsAsFactors = FALSE)
winter_weather <- read.csv("winter_weather.csv", stringsAsFactors = FALSE)

glimpse(summer_weather)
glimpse(winter_weather)

```

## Data munging
Recalculate in CELSIUS using weathermetrics package

```{r}

library(weathermetrics)


summer_weather <- summer_weather %>% 
                    mutate(tmpc = convert_temperature(tmpf,
                                                      old_metric = "f", 
                                                      new_metric = "c"),
                           dwpc = convert_temperature(dwpf,
                                                      old_metric = "f",
                                                      new_metric = "c"))

winter_weather <- winter_weather %>% 
  mutate(tmpc = convert_temperature(tmpf,
                                    old_metric = "f", 
                                    new_metric = "c"))

```


Calculate the Humidex with the calcHumx() function in the comf package!

```{r calculate humidex and avg winter temp}
library(comf)

summer_weather <- summer_weather %>% 
                    mutate(humidex = calcHumx(ta = tmpc, rh = dwpc))

summer_data <- summer_weather %>% 
                 group_by(station) %>% 
                 summarize(summer_humidex = mean(humidex, na.rm = TRUE))

winter_data <- winter_weather %>% 
                 group_by(station) %>% 
                 summarize(winter_avg_temp = mean(tmpc, na.rm = TRUE))

```

Join together using `left_join()` operation!

```{r}

climate_japan <- left_join(summer_data, winter_data, by = "station")

glimpse(climate_japan)

```

Add in city names through airport code data set

```{r}

climate_japan <- left_join(climate_japan, jp_airport_codes,
                           by = c("station" = "ICAO"))

glimpse(climate_japan)

```

hmm... remove Narita as not really TOKYO >>> far out in Chiba
Haneda is more representative of Tokyo's weather, although it is stuck out in Tokyo Bay

```{r}
# Remove Narita airport observation row
climate_japan <- climate_japan %>% filter(station != "RJAA")

# Remove Kansai International >>> handles all internatonal flights, ~20 miles away from Osaka
climate_japan <- climate_japan %>% filter(station != "RJBB")

glimpse(climate_japan)

```



```{r}
# Ibaraki Aiport from Tokyo to Ibaraki
climate_japan$City[climate_japan$station == "RJAH"] <- "Ibaraki"

# Kochi, Kochi to just Kochi
climate_japan$City[climate_japan$station == "RJOK"] <- "Kochi"

glimpse(climate_japan)

```



```{r}
# just use CITY as the labels instead or clog up the graph...
# climate_japan <- climate_japan %>% unite(Label, City, Airport, sep = " - ", remove = TRUE)

# Iwakuni appears twice for some reason...
climate_japan <- climate_japan %>% unique()

```



## Plotting!

Now let's plot! Well, before that we have to install the **xkcd** font and package. Installing fonts can be a bit difficult but 
>>
>>>
>>>>

Now we are ready!

```{r}
library(ggplot2)
library(ggrepel)
library(xkcd)
library(extrafont)

xrange <- range(climate_japan$summer_humidex)
yrange <- range(climate_japan$winter_avg_temp)

set.seed(42)

climate_japan %>% 
  ggplot(aes(summer_humidex, winter_avg_temp)) +
  geom_point() +
  geom_text_repel(aes(label = City), 
                  family = "xkcd",
                  max.iter = 50000) +
  ggtitle("Where to live based on your temperature preferences",
          subtitle = "Data from airport weather stations 2016-2017") +
  xlab("Humidex: summer heat & humidity") +
  ylab("Avg. winter temperature - Celsius") +
  xkcdaxis(xrange = xrange,
           yrange = yrange) +
  theme_xkcd() +
  theme(text = element_text(size = 16, family = "xkcd"))

# need to fix city text >>> elongation vowels symbols in text
# >>> 12 hours later, rerun, elongation vowels not in anymore???

# oddly, the graph looks like a map of Japan... with cities in Hokkaido in the bottom right 
# instead of the top right, vice-versa for Okinawa!
# >>> see this much better on a bigger screen: screenshot

```


```{r}
# MAP of JAPAN:
library(ggplot2)

# acquire lon-lat of Japan from map_data()
JPN <- map_data(map = "world", region = "Japan")

# join lon-lat data into climate_japan
lat_lon <- summer_weather %>% 
  group_by(station) %>% 
  summarize(lat = mean(lat), lon = mean(lon))

# i'm sure there is a better way to do this???

climate_japan_map <- left_join(climate_japan, lat_lon, by = "station") 

glimpse(climate_japan_map)

climate_japan_map %>% 
  ggplot(aes(lon, lat)) +
  geom_point(aes(color = winter_avg_temp), size = 2.5) +
  geom_text_repel(aes(label = City),
                  family = "xkcd", size = 3,
                  max.iter = 50000) +
  geom_polygon(data = JPN, aes(x = long, y = lat, group = group), 
               fill = NA, color = "black") +
  coord_map() +
  labs(title = "Avg. Winter Temperature in Japan",
       subtitle = "Data from RIEM 2016-2017",
       x = "", y = "") +
  theme_xkcd() +
  theme(text = element_text(family = "xkcd", size = 14))

```



# filter out below 30 lat
# >>> make separate for Okinawa + Ryukyu Islands for create space

```{r}

glimpse(JPN)

```


```{r}
# Blues set colors:
colorRampPalette(brewer.pal(n = 9, name = "Blues"))(9)
# Red set colors:



# Winter avg. temp: ####

climate_japan_map %>% 
  filter(lat > 30) %>% 
  ggplot(aes(lon, lat)) +
  geom_point(aes(color = winter_avg_temp), size = 3.5) +
  geom_text_repel(aes(label = City),
                  family = "xkcd", size = 4.5,
                  max.iter = 50000) +
  geom_polygon(data = JPN %>% filter(lat > 30), aes(x = long, y = lat, group = group), 
               fill = NA, color = "black") +
  coord_map() +
  labs(title = "Avg. Winter Temperature in Japan",
       subtitle = "Data from RIEM 2016-2017",
       x = "", y = "") +
  theme_xkcd() +
  theme(text = element_text(family = "xkcd", size = 14)) +
  scale_color_gradient(low = "#08306B")

# Humidex: ####

climate_japan_map %>% 
  filter(lat > 30) %>% 
  ggplot(aes(lon, lat)) +
  geom_point(aes(color = summer_humidex), size = 3.5) +
  geom_text_repel(aes(label = City),
                  family = "xkcd", size = 4.5,
                  max.iter = 50000) +
  geom_polygon(data = JPN_1, aes(x = long, y = lat, group = group), 
               fill = NA, color = "black") +
  coord_map() +
  labs(title = "Avg. Winter Temperature in Japan",
       subtitle = "Data from RIEM 2016-2017",
       x = "", y = "") +
  theme_xkcd() +
  theme(text = element_text(family = "xkcd", size = 14)) +
  scale_color_gradient(low = "#08306B")

```


```{r}
# Okinawa and Ryukyu Islands
Okinawa_Ryukyu <- JPN %>% filter(lat < 30)

climate_japan_map %>% 
  filter(lat < 30) %>% 
  ggplot(aes(lon, lat)) +
  geom_point(aes(color = winter_avg_temp), size = 3.5) +
  geom_text_repel(aes(label = City),
                  family = "xkcd", size = 4.5,
                  max.iter = 50000) +
  geom_polygon(data = JPN %>% filter(lat < 30), aes(x = long, y = lat, group = group), 
               fill = NA, color = "black") +
  coord_map() +
  labs(title = "Avg. Winter Temperature in Japan",
       subtitle = "Data from RIEM 2016-2017",
       x = "", y = "") +
  theme_xkcd() +
  theme(text = element_text(family = "xkcd", size = 14)) +
  scale_color_gradient(low = "#08306B")

```


```{r}
# Leaflet ####

# Tourist areas:

tour <- data_frame(
  location = c("Hokkaido", "Tohoku", "Tokyo", "Osaka", 
               "Kobe", "Shikoku", "Hiroshima", "Kyushu", "Okinawa"),
  City = c("Sapporo", "Aomori", "Tokyo", "Osaka", "Kobe", 
           "Kochi", "Hiroshima", "Matsuyama", "Naha")
)

tour <- left_join(tour, climate_japan_map, by = "City")

# Not have Kanazawa, Kyoto, and Nara >>> just have to manually add in i guess?
# won't let me do all 3 at once...

Kanazawa <- ggmap::geocode("Kanazawa", output = "latlon")
Kyoto <- ggmap::geocode("Kyoto", output = "latlon")
Nara <- ggmap::geocode("Nara", output = "latlon")

missing_tour <- rbind(Kanazawa, Kyoto, Nara)

missing_tour <- missing_tour %>% mutate(City = c("Kanazawa", "Kyoto", "Nara"))

missing_tour

tour <- full_join(missing_tour, tour)

# not have to run geocode each time:
write.csv(tour, "~/R_materials/japan_weather_xkcd/tour.csv")

tour <- read.csv("tour.csv", stringsAsFactors = FALSE)

```


```{r}
library(leaflet)

leaflet(climate_japan_map) %>% 
  addTiles() %>% 
  setView(lng = 137.7, lat = 36.5, zoom = 6) %>% 
  addCircles(lng = ~lon, lat = ~lat, radius = 5000, color = "#09f") %>% 
  addMarkers(lng = ~lon, lat = ~lat, 
             popup = paste("Winter Avg.(Celsius):",
               round(climate_japan_map$winter_avg_temp, 2), 
               " | ",
               "Summer Humidex:",
               round(climate_japan_map$summer_humidex, 2)),
             label = ~City
             ) %>% 
  addMarkers(lng = ~tour$lon, lat = ~tour$lat)

```





